SUPPLEMENTARY INFORMATION: NMRlipids Databank makes data-driven analysis of biomembrane properties accessible for all

### 2023-01-27 SI.tex
Updates from Overleaf

\clearpage
%\section{Experimental data}
\section{NMR experiments}
Acyl chain order parameters of POPE and POPG were analyzed from the experiments that were previosly used to determine headgroup order parameters~\cite{bacle21}. The analysis of the crowded spectral region at 29-31 ppm was based on the previous assignment reported for POPC membranes~\cite{ferreira13}.

>>>>

\clearpage
%\section{Experimental data}
\section{NMR experiments}
Acyl chain order parameters of POPE and POPG were analyzed from the experiments that were previously used to determine headgroup order parameters~\cite{bacle21}. The analysis of the crowded spectral region at 29-31 ppm was based on the previous assignment reported for POPC membranes~\cite{ferreira13}.
